Score-based tests of measurement invariance: Use in practice

### 2014-02-19 frontiers/IMPS.Rnw
Final modifications to frontiers prior to resubmission, and addition of IMPS abstract.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@318 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\abstract{
In this paper, we consider a family of  recently-proposed measurement invariance
tests that are based on the {\em scores} of a fitted model.  This family can be used
to test for measurement invariance w.r.t.\ a continuous auxiliary variable,
without pre-specification of subgroups. Moreover, the family can be used when
one wishes to test for  measurement invariance w.r.t.\ an ordinal auxiliary
variable, yielding test statistics that are sensitive to violations that are
monotonically related to the ordinal variable (and less sensitive to
non-monotonic violations).  The paper is specifically aimed at potential users
of the tests who may wish to know (i) how the tests can be employed for their
data, and (ii) whether the tests can accurately identify specific models parameters that violate measurement invariance (possibly in the presence of model misspecification).  After providing an
overview of the tests, we illustrate their general use via the \proglang{R} packages \pkg{lavaan}
and \pkg{strucchange}.  We then describe two novel simulations that provide evidence
of the tests' practical abilities.  As a whole, the paper provides researchers
with the tools and knowledge needed to apply these tests to general measurement
invariance scenarios.
}

\acknowledgements{This work was supported by National Science
  Foundation grant SES-1061334. 
  Correspondence to Edgar Merkle. 
  Email: merklee@missouri.edu.}
\shorttitle{Score-based tests in practice}
\rightheader{Score-based tests in practice}

\newcommand{\argmax}{\operatorname{argmax}\displaylimits}
\let\proglang=\textsf
\let\pkg=\emph
\let\code=\texttt

%% for internal use
\newcommand{\fixme}[1]{\emph{\marginpar{FIXME} (#1)}}
\newcommand{\readme}[1]{\emph{\marginpar{Ed} (#1)}}
\newcommand{\seeme}[1]{\emph{\marginpar{Ting} (#1)}}

>>>>

\abstract{
In this presentation, we study a family of  recently-proposed measurement invariance
tests that are based on the {\em scores} of a fitted model.  This family can be used
to test for measurement invariance w.r.t.\ a continuous auxiliary variable,
without pre-specification of subgroups. Moreover, the family can be used when
one wishes to test for  measurement invariance w.r.t.\ an ordinal auxiliary
variable, yielding test statistics that are sensitive to violations that are
monotonically related to the ordinal variable (and less sensitive to
non-monotonic violations).  After providing an overview of the family
of tests, we present new simulation-based results examining (i) the extent
to which the tests can identify specific parameters violating
measurement invariance, and (ii) the extent to which the tests are
impacted by model misspecification.
We also describe an R implementation that allows users to generally
apply the tests to SEMs estimated under multivariate normality.
}

% \acknowledgements{This work was supported by National Science
%   Foundation grant SES-1061334. 
%   Correspondence to Edgar Merkle. 
%   Email: merklee@missouri.edu.}
% \shorttitle{Score-based tests in practice}
% \rightheader{Score-based tests in practice}

\let\proglang=\textsf
\let\pkg=\emph
\let\code=\texttt

### 2014-02-19 frontiers/Supple_Material.Rnw
Final modifications to frontiers prior to resubmission, and addition of IMPS abstract.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@318 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\maketitle

@@

\section{Appendix}

This Appendix contains additional results from Simulation 2, where there existed
model misspecification (lacking one loading from Scale 1 to
Math). Figures~\ref{fig:sim22res} to~\ref{fig:sim26res} display
results when the unmodeled loading, the loading $\lambda_{11}$, the
covariance $\phi_{12}$, the error term $\psi_{11}$, and the intercept $\mu_{11}$
violate invariance, respectively.  Results are only shown for simulation
conditions exhibiting power curves that increased from zero.  These
results were generally the same as the Simulation 1 results.

>>>>

%\maketitle

@@

\section{Supplementary Material to Wang, Merkle, \& Zeileis}

The Supplementary Material contains additional results from Simulation
2, where there existed 
model misspecification (lacking one loading from Scale 1 to
Math). Figures~\ref{fig:sim22res} to~\ref{fig:sim26res} display
results when the unmodeled loading, the loading $\lambda_{11}$, the
covariance $\phi_{12}$, the error term $\psi_{11}$, and the intercept $\mu_{11}$
violate invariance, respectively.  Results are only shown for simulation
conditions exhibiting power curves that increased from zero.  These
results were generally the same as the Simulation 1 results.

### 2014-02-19 frontiers/frontiers.Rnw
minimal touch-ups in the wording
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@316 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
Final modifications to frontiers prior to resubmission, and addition of IMPS abstract.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@318 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

In this section, we demonstrate how the above tests can be carried out in \proglang{R}, 
using the package \pkg{lavaan} \cite{lavaan11} for model estimation and \pkg{strucchange} 
\cite{ZeiLei02,Zei06} for testing.  We use data from \citeA{FroFan11} concerning 
the applicability of adult gratitude scales to youth, available in the~\proglang{R} 
package \pkg{psychotools} \cite{zeilei12}.  The data consist of responses to three adult 
gratitude scales from $n=1401$ youth aged 10--19 years. 
The original authors 
were specifically interested in whether the scales were measurement invariant 
across age.  Because the sample size at each age was unbalanced, the authors 
created age groups of approximately equal sample size.  In the examples below, 
we test for measurement invariance across these age groups.
For illustrative purposes, we conduct multiple tests and
compare them to the traditional significance level of .05.  In
practice, however, one should generally adjust the significance level
for the number of tests carried out.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Power and Type I error were examined across three sample sizes
($n=120,480,960$), three numbers of categories ($m=4,8,12$), and
17 magnitudes of invariance violations (described in the following sentences). 
The measurement invariance violations began at level $1+m/2$ of the
auxiliary variable $V$ and were consistent thereafter: individuals below
level $1+m/2$ of $V$ deviated from individuals at or above level $1+m/2$ 
by $d$ times the parameters' asymptotic standard errors
(scaled by $\sqrt n$), with $d=0,0.25,0.5,...,4$. 
For each combination of sample size ($n$) $\times$ violation
magnitude ($d$) $\times$ violating parameter $\times$ categories ($m$), 5000 datasets were
generated and tested.  Statistics from Equations~\eqref{eq:wdm}, \eqref{eq:maxlmo}
and~\eqref{eq:lmuo} were examined. As mentioned previously,
\eqref{eq:lmuo} is asymptotically equivalent to the usual likelihood
ratio test.  Thus, this statistic provides information about the
relative performance of the ordinal statistics vs.\ the LRT.

In all conditions, we maintained equal sample 
sizes in each subgroup of the ordinal variable.

@@

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  A subset of results is displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type
I error is also observed when testing all loadings and all unique
variances (see the Appendix).  Tests
associated with the factor 
covariance and intercept did not demonstrate this error, however.  In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

When the parameter violating measurement invariance was modeled,
results were generally the same as Simulation 1.  
When the modeled factor loading, $\lambda_{11}$, violated measurement
invariance, the statistics were generally able to pick up the violation despite
the misspecification. Similar results were observed
when the unique variance, intercept and factor covariance parameters violated measurement
invariance; these results are all shown in the Appendix.
In particular, power of the ordered statistics was higher than power
of the unordered statistic in 
each panel.

In summary, the proposed test statistics appear robust to unmodeled
loading parameters, so long 
as the unmodeled loading does not violate measurement invariance.  If
the unmodeled loading  
does violate measurement invariance, the tests can still detect
measurement invariance violations.  The violations are assigned to 
modeled parameters that do not violate measurement invariance, however.
The impacted parameters include the error 
variance and other loadings associated with the manifest variable that
has an unmodeled loading.
Thus, as for other tests of measurement invariance, it is important to
study the extent to 
which the hypothesized model includes all parameters of importance
(i.e., the extent to which the model is well specified).

@@

\section{Appendix}

This Appendix contains additional results from Simulation 2, where there existed
model misspecification (lacking one loading from Scale 1 to
Math). Figures~\ref{fig:sim22res} to~\ref{fig:sim26res} display
results when the unmodeled loading, the loading $\lambda_{11}$, the
covariance $\phi_{12}$, the error term $\psi_{11}$, and the intercept $\mu_{11}$
violate invariance, respectively.  Results are only shown for simulation
conditions exhibiting power curves that increased from zero.  These
results were generally the same as the Simulation 1 results.

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
parameter violating measurement invariance is the unmodeled
loading. Panel labels denote the parameter(s) 
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim22res}
<<sim22res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
		 pars %in% c("All Loadings", "All Errors", "All Intercepts") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)", ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(5, 6, 7)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
parameter violating measurement invariance is $\lambda_{11}$.  Panel
labels denote the parameter(s)  
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim23res}
<<sim23res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms=="extra+loading" & 
		 pars %in% c("Loading1", "All Loadings") & diff %% 0.5 == 0),
       type = "b", xlab = expression(paste("Violation Magnitude (", lambda[11], ")")), ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(1, 5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
parameter violating measurement invariance is $\phi_{12}$.  Panel
labels denote the parameter  
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim24res}
<<sim24res, fig=TRUE, height=4.5, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms=="extra+var" & 
		 pars %in% c("Covariance") & diff %% 0.5 == 0),
       type = "b", xlab = expression(paste("Violation Magnitude (", phi[12], ")")),
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(2, 4:5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
parameter violating measurement invariance is $\psi_{11}$.  Panel
labels denote the parameter(s)  
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim25res}
<<sim25res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra+error" & 
		 pars %in% c("Error1", "All Errors") & diff %% 0.5 == 0),
       type = "b", xlab = expression(paste("Violation Magnitude (", psi[11], ")")),
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(3,6)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
parameter violating measurement invariance is $\mu_{11}$.  Panel
labels denote the parameter(s)  
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim26res}
<<sim26res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra+intercept" & 
		 pars %in% c("Intercept1", "All Intercepts") & diff %% 0.5 == 0),
       type = "b", xlab = expression(paste("Violation Magnitude (", mu[11], ")")),
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(4,7)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

>>>>

In this section, we demonstrate how the above tests can be carried out in \proglang{R}, 
using the package \pkg{lavaan} \cite{lavaan11} for model estimation and \pkg{strucchange} 
\cite{ZeiLei02,Zei06} for testing.  We use data from \citeA{FroFan11} concerning 
the applicability of adult gratitude scales to youth, available in the~\proglang{R} 
package \pkg{psychotools} \cite{zeilei12}.  The data consist of responses to three adult 
gratitude scales from $n=1401$ youth aged 10--19 years. 
The original authors 
were specifically interested in whether the scales were measurement invariant 
across age.  Because the sample size at each age was unbalanced, the authors 
created age groups of approximately equal sample size.  In the examples below, 
we test for measurement invariance across these age groups.
For illustrative purposes, we conduct multiple tests and
compare them to the traditional significance level of 0.05.  In
practice, however, one should generally adjust the significance level
for the number of tests carried out.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Power and Type I error were examined across three sample sizes
($n=120,480,960$), three numbers of categories ($m=4,8,12$), and
17 magnitudes of invariance violations (described in the following sentences). 
The measurement invariance violations began at level $1+m/2$ of the
auxiliary variable $V$ and were consistent thereafter: individuals below
level $1+m/2$ of $V$ deviated from individuals at or above level $1+m/2$ 
by $d$ times the parameters' asymptotic standard errors
(scaled by $\sqrt n$), with $d=0,0.25,0.5,...,4$ (see replication code
for specific values of the standard errors).
For each combination of sample size ($n$) $\times$ violation
magnitude ($d$) $\times$ violating parameter $\times$ categories ($m$), 5000 datasets were
generated and tested.  Statistics from Equations~\eqref{eq:wdm}, \eqref{eq:maxlmo}
and~\eqref{eq:lmuo} were examined. As mentioned previously,
\eqref{eq:lmuo} is asymptotically equivalent to the usual likelihood
ratio test.  Thus, this statistic provides information about the
relative performance of the ordinal statistics vs.\ the LRT.

In all conditions, we maintained equal sample 
sizes in each subgroup of the ordinal variable.  Aside from the
parameter changes that reflect measurement invariance, the fitted
models matched the data generating model.

@@

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  A subset of results is displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type
I error is also observed when testing all loadings and all unique
variances (see the Supplementary Material).  Tests
associated with the factor 
covariance and intercept did not demonstrate this error, however.  In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

When the parameter violating measurement invariance was modeled,
results were generally the same as Simulation 1.  
When the modeled factor loading, $\lambda_{11}$, violated measurement
invariance, the statistics were generally able to pick up the violation despite
the misspecification. Similar results were observed
when the unique variance, intercept and factor covariance parameters violated measurement
invariance; these results are all shown in the Supplementary Material.
In particular, power of the ordered statistics was higher than power
of the unordered statistic in 
each panel.

In summary, the proposed test statistics appear robust to unmodeled
loading parameters, when
the unmodeled loading does not violate measurement invariance and when
the rest of the model is correctly specified (save for the measurement
invariance violation).  If
the unmodeled loading  
does violate measurement invariance, the tests can still detect
measurement invariance violations.  The violations are assigned to 
modeled parameters that do not violate measurement invariance, however.
The impacted parameters include the error 
variance and other loadings associated with the manifest variable that
has an unmodeled loading.
Thus, as for other tests of measurement invariance, it is important to
study the extent to 
which the hypothesized model includes all parameters of importance
(i.e., the extent to which the model is well specified).

@@

%% \section{Appendix}

%% This Appendix contains additional results from Simulation 2, where there existed
%% model misspecification (lacking one loading from Scale 1 to
%% Math). Figures~\ref{fig:sim22res} to~\ref{fig:sim26res} display
%% results when the unmodeled loading, the loading $\lambda_{11}$, the
%% covariance $\phi_{12}$, the error term $\psi_{11}$, and the intercept $\mu_{11}$
%% violate invariance, respectively.  Results are only shown for simulation
%% conditions exhibiting power curves that increased from zero.  These
%% results were generally the same as the Simulation 1 results.

%% \begin{figure}
%% \caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
%% violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
%% parameter violating measurement invariance is the unmodeled
%% loading. Panel labels denote the parameter(s) 
%% being tested and the number of levels of the ordinal variable $m$.}
%% \label{fig:sim22res}
%% <<sim22res, fig=TRUE, height=7, width=9, echo=FALSE>>=
%% trellis.par.set(theme = canonical.theme(color = FALSE))
%% mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
%% xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
%%        subset = (parms == "extra" & 
%% 		 pars %in% c("All Loadings", "All Errors", "All Intercepts") & diff %% 0.5 == 0),
%%        type = "b", xlab = "Violation Magnitude (Unmodeled Loading)", ylab = "Power", key = mykey, as.table = TRUE,
%%        strip = function(..., which.given, factor.levels){
%% 	   if(which.given == 2){
%% 	       strip.default(which.given, factor.levels = parlabs[c(5, 6, 7)], ...)
%% 	   } else {
%% 	       strip.default(which.given, factor.levels = factor.levels, ...)
%% 	   }
%%        })
%% @

%% \end{figure}

%% \begin{figure}
%% \caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
%% violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
%% parameter violating measurement invariance is $\lambda_{11}$.  Panel
%% labels denote the parameter(s)  
%% being tested and the number of levels of the ordinal variable $m$.}
%% \label{fig:sim23res}
%% <<sim23res, fig=TRUE, height=7, width=9, echo=FALSE>>=
%% trellis.par.set(theme = canonical.theme(color = FALSE))
%% mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
%% xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
%%        subset = (parms=="extra+loading" & 
%% 		 pars %in% c("Loading1", "All Loadings") & diff %% 0.5 == 0),
%%        type = "b", xlab = expression(paste("Violation Magnitude (", lambda[11], ")")), ylab = "Power", key = mykey, as.table = TRUE,
%%        strip = function(..., which.given, factor.levels){
%% 	   if(which.given == 2){
%% 	       strip.default(which.given, factor.levels = parlabs[c(1, 5)], ...)
%% 	   } else {
%% 	       strip.default(which.given, factor.levels = factor.levels, ...)
%% 	   }
%%        })
%% @

%% \end{figure}

%% \begin{figure}
%% \caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
%% violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
%% parameter violating measurement invariance is $\phi_{12}$.  Panel
%% labels denote the parameter  
%% being tested and the number of levels of the ordinal variable $m$.}
%% \label{fig:sim24res}
%% <<sim24res, fig=TRUE, height=4.5, width=9, echo=FALSE>>=
%% trellis.par.set(theme = canonical.theme(color = FALSE))
%% mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
%% xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
%%        subset = (parms=="extra+var" & 
%% 		 pars %in% c("Covariance") & diff %% 0.5 == 0),
%%        type = "b", xlab = expression(paste("Violation Magnitude (", phi[12], ")")),
%%        ylab = "Power", key = mykey, as.table = TRUE,
%%        strip = function(..., which.given, factor.levels){
%% 	   if(which.given == 2){
%% 	       strip.default(which.given, factor.levels = parlabs[c(2, 4:5)], ...)
%% 	   } else {
%% 	       strip.default(which.given, factor.levels = factor.levels, ...)
%% 	   }
%%        })
%% @

%% \end{figure}

%% \begin{figure}
%% \caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
%% violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
%% parameter violating measurement invariance is $\psi_{11}$.  Panel
%% labels denote the parameter(s)  
%% being tested and the number of levels of the ordinal variable $m$.}
%% \label{fig:sim25res}
%% <<sim25res, fig=TRUE, height=7, width=9, echo=FALSE>>=
%% trellis.par.set(theme = canonical.theme(color = FALSE))
%% mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
%% xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
%%        subset = (parms == "extra+error" & 
%% 		 pars %in% c("Error1", "All Errors") & diff %% 0.5 == 0),
%%        type = "b", xlab = expression(paste("Violation Magnitude (", psi[11], ")")),
%%        ylab = "Power", key = mykey, as.table = TRUE,
%%        strip = function(..., which.given, factor.levels){
%% 	   if(which.given == 2){
%% 	       strip.default(which.given, factor.levels = parlabs[c(3,6)], ...)
%% 	   } else {
%% 	       strip.default(which.given, factor.levels = factor.levels, ...)
%% 	   }
%%        })
%% @

%% \end{figure}

%% \begin{figure}
%% \caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
%% violations of 0--4 standard errors (scaled by $\sqrt{n}$), Simulation 2. The
%% parameter violating measurement invariance is $\mu_{11}$.  Panel
%% labels denote the parameter(s)  
%% being tested and the number of levels of the ordinal variable $m$.}
%% \label{fig:sim26res}
%% <<sim26res, fig=TRUE, height=7, width=9, echo=FALSE>>=
%% trellis.par.set(theme = canonical.theme(color = FALSE))
%% mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
%% xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
%%        subset = (parms == "extra+intercept" & 
%% 		 pars %in% c("Intercept1", "All Intercepts") & diff %% 0.5 == 0),
%%        type = "b", xlab = expression(paste("Violation Magnitude (", mu[11], ")")),
%%        ylab = "Power", key = mykey, as.table = TRUE,
%%        strip = function(..., which.given, factor.levels){
%% 	   if(which.given == 2){
%% 	       strip.default(which.given, factor.levels = parlabs[c(4,7)], ...)
%% 	   } else {
%% 	       strip.default(which.given, factor.levels = factor.levels, ...)
%% 	   }
%%        })
%% @

%% \end{figure}
